\bf\mftitle

### 2011-03-01 doc/jInfer/architecture/architecture.tex
Removed XSDImport module from list of dependants on RuleDisplayer token.

\paragraph{}
Another use of tokens is \code{cz.cuni.mff.ksi.jinfer.base.interfaces.RuleDisplayer} representing a module providing a rule displayer. This token is provided by \jmodule{BasicRuleDisplayer} and \jmodule{TreeRuleDisplayer}, requested by \jmodule{BasicIGG}, \jmodule{XSDImporter} and \jmodule{TwoStepSimplifier}.

>>>>

\paragraph{}
Another use of tokens is \code{cz.cuni.mff.ksi.jinfer.base.interfaces.RuleDisplayer} representing a module providing a rule displayer. This token is provided by \jmodule{BasicRuleDisplayer} and \jmodule{TreeRuleDisplayer}, requested by \jmodule{BasicIGG} and \jmodule{TwoStepSimplifier}.
